### 2020-06-12 chapters/sota.tex
DABA pseudocode

        \Function{insert}{B, v}
            \State{B.push(v, getStackAggregationValue(B) $\oplus$ v}
        \EndFunction

@@

            \If{F.isEmpty()} \Comment{// Flip B onto F and update aggregation value}
                \While {\textbf{not} B.isEmpty()}
                    \State{F.push(B.top().val, B.top().val $\oplus$ getStackAggregationValue(F))}
                    \State{B.pop()}
                \EndWhile
            \EndIf
            \State{F.pop()}
        \EndFunction
    \end{algorithmic}
\end{algorithm}

@@

DABA uses two queues, \textit{vals} and \textit{aggs}, both of size \textit{n}, seen in Figure \ref{fig:daba-ds}. Both queues share six pointers --- \textit{F, L, R, A, B} and \textit{E} --- that point to the same position for each queue. These pointers are always ordered as follows: $\textit{F} \leq \textit{L} \leq \textit{R} \leq \textit{A} \leq \textit{B} \leq \textit{E}.$

@@

Figure \ref{fig:pseudo-daba} shows the pseudocode presented by the authors for the DABA algorithm. In reality, after each insertion and eviction, besides the procedure already described, function \textit{fixup} is executed. The \textit{fixup} function performs the incremental reversal of \textit{l\textsubscript{B}} to \textit{l\textsubscript{F}}. The pseudocode \ref{fig:pseudo-daba} shows how such reversal is done but we will not elaborate on such procedure. However, it is important to stress out that this is the core idea of DABA: avoid occasional expensive operations, like Two-Stacks' \textit{flip}, by spreading them out across run time, in the form of DABA's \textit{fixup}.

\begin{figure}[!htb]
    \begin{center}
      \includegraphics[scale=0.7]{figures/daba-pseudocode.png}
      \caption{DABA algorithm}
      \label{fig:pseudo-daba}
    \end{center}
\end{figure}

@@

\subsection*{Applicability to our Hypothesis}
Even though DABA improves on the time complexity of Two-Stacks, it still shows linear space complexity regarding window size. In our monitoring system, we need to analyze large windows of data, requiring at least logarithmic space complexity, thus making DABA inapplicable for our Hypothesis.

>>>>

        \Function{insert}{B, v}
            \State{B.push( (v, getStackAggregationValue(B) $\oplus$ v) )}
        \EndFunction

@@

            \If{F.isEmpty()} \Comment{// Flip B onto F and update top aggregation value}
                \While {\textbf{not} B.isEmpty()}
                    \State{F.push(B.top().val, B.top().val $\oplus$ getStackAggregationValue(F))}
                    \State{B.pop()}
                \EndWhile
            \EndIf
            \State{F.pop()}
        \EndFunction
    \end{algorithmic}
\end{algorithm}

@@

DABA uses two queues, \textit{vals} and \textit{aggs}, both of size \textit{n}, seen in Figure \ref{fig:daba-ds}, which was directly taken from \textit{"Low-Latency Sliding-Window Aggregation in Worst-Case Constant Time"} by Tangwongsan et. al. Both queues share six pointers --- \textit{F, L, R, A, B} and \textit{E} --- that point to the same position for each queue. These pointers are always ordered as follows: $\textit{F} \leq \textit{L} \leq \textit{R} \leq \textit{A} \leq \textit{B} \leq \textit{E}.$

@@

Algorithm \ref{pseudo:daba} shows the pseudocode presented by the authors for the DABA algorithm. In reality, after each insertion and eviction, besides the procedure already described, function \textit{fixup} is executed. The \textit{fixup} function performs the incremental reversal of \textit{l\textsubscript{B}} to \textit{l\textsubscript{F}}. Algorithms \ref{pseudo:daba-helpers} and \ref{pseudo:daba} show how such reversal is done but we will not elaborate on such procedure. However, it is important to stress out that this is the core idea of DABA: avoid occasional expensive operations, like Two-Stacks' \textit{flip}, by spreading them out across run time, in the form of DABA's \textit{fixup}.

\begin{algorithm}
    \caption{DABA helper functions}
    \label{pseudo:daba-helpers}
    \begin{algorithmic}[1]
        \Function{getListFAggregationValue}{}
            \If{F == B}
                \State \Return{$\overline{\theta}$}
            \Else
                \State \Return{aggs[F]}
            \EndIf
        \EndFunction

        \Function{getListBAggregationValue}{}
            \If{B == E}
                \State \Return{$\overline{\theta}$}
            \Else
                \State \Return{aggs[E - 1]}
            \EndIf
        \EndFunction

        \Function{getListLAggregationValue}{}
            \If{L == R}
                \State \Return{$\overline{\theta}$}
            \Else
                \State \Return{aggs[L]}
            \EndIf
        \EndFunction

        \Function{getListRAggregationValue}{}
            \If{R == A}
                \State \Return{$\overline{\theta}$}
            \Else
                \State \Return{aggs[A - 1]}
            \EndIf
        \EndFunction

        \Function{getListAAggregationValue}{}
            \If{A == B}
                \State \Return{$\overline{\theta}$}
            \Else
                \State \Return{aggs[A]}
            \EndIf
        \EndFunction

    \end{algorithmic}
\end{algorithm}

\begin{algorithm}
    \caption{DABA insert, evict and query methods}
    \label{pseudo:daba}
    \begin{algorithmic}[1]
        \Function{query}{}
            \State \Return{getListFAggregationValue() $\oplus$ getListBAggregationValue()}
        \EndFunction

        \Function{insert}{v}
            \State vals.pushBack(v)
            \State aggs.pushBack(getListBAggregationValue() $\oplus$ v)
            \State fixup()
        \EndFunction

        \Function{evict}{}
            \State vals.popFront()
            \State aggs.popFront()
            \State fixup()
        \EndFunction

        \Function{fixup}{}
        \If{F == B}
            \State $B \gets E$
            \State $A \gets E$
            \State $R \gets E$
            \State $L \gets E$
        \Else
            \If{L == B}
                \State $L \gets F$
                \State $A \gets E$
                \State $B \gets E$
            \EndIf
            \If{L == R}
                \State $A \gets A + 1$
                \State $R \gets R + 1$
                \State $L \gets L + 1$
            \Else
                \State $aggs[L] \gets getListLAggregationValue() \oplus getListRAggregationValue() \oplus getListAAggregationValue()$
                \State $L \gets L + 1$
                \State $aggs[A - 1] \gets vals[A - 1] \oplus getListAAggregationValue()$
                \State $A \gets A - 1$
            \EndIf
        \EndIf
        \EndFunction
    \end{algorithmic}
\end{algorithm}

@@

\subsection*{Applicability to our Hypothesis}
Even though DABA improves on the time complexity of Two-Stacks, it still shows linear space complexity regarding window size. In our monitoring system, we need to analyze large windows of data, thus making DABA inapplicable for our Hypothesis.
